Archive

### 2023-05-26 Manuscript/Imputation_of_Incomplete_Multilevel_Data.Rmd
Feedback

@@

- `region` Cluster variable,
- `gender` Gender (0=male, 1=female),
- `age` Age of the patient,
- `height` Height in meters,
- `weight` Weight in kilograms,
- `rt`` Response time in minutes (inclusion-restriction variable).

@@

Create predictor matrix:
```{r obesity-pred}
pred <- quickpred(dat)   # predictor matrix
pred["Weight","Cluster"]<- -2 # clustering variable
pred["Weight", ] <- -3 #inclusion-restriction variable
plot_pred(pred)
```

@@

<!-- - JOMO in \pkg{mice} -> on the side for now -->
<!-- # look at jomo for categorical variables? -->
<!-- # semi-cont with jomo is not ideal (schafer, '97) because you need 2-step approach -->
<!-- # pmm is better (more efficient) because it will still look for donors (maybe outside of cluster) based on predictive distance, even for very small clusters -->
<!-- # make assumptions of these methods explicit! -->

@@

There are different strategies that can be adopted in the imputation process that account for clustering: inclusion of cluster indicator variable, performing a separate imputation process for each cluster, or performing a simultaneous imputation process by using an imputation method that accounts for clustering.(Stata: https://www.stata.com/support/faqs/statistics/clustering-and-mi-impute/)

@@

Under this hierarchical imputation model, observations within clusters are correlated and this correlation is modelled by a random effect so the hierarchical model can be estimated even when there are few observations per cluster. However, this strategy is best suited for balanced data (Grund, 2017) and when random effects model is appropriated, i.e. the number of clusters is adequate. (Austin,2018).

>>>>

TODO: explain exclusion restriction.

@@

- `region` Cluster variable,
- `gender` Gender (0=male, 1=female),
- `age` Age of the patient,
- `height` Height in meters,
- `weight` Weight in kilograms,
- `time`` Response time in minutes (inclusion-restriction variable).

@@

The matrix only shows the predictors for the main model, not the selection model.

Create predictor matrix:
```{r obesity-pred}
pred <- quickpred(dat)   # predictor matrix
pred[,"Cluster"]<- -2 # clustering variable
pred[, "Weight"] <- -3 #inclusion-restriction variable
plot_pred(pred)
```

@@

<!-- - JOMO in \pkg{mice} -> on the side for now -->
<!-- # look at jomo for categorical variables? -->
<!-- # semi-cont with jomo is not ideal (schafer, '97) because you need 2-step approach -->
<!-- # pmm is better (more efficient) because it will still look for donors (maybe outside of cluster) based on predictive distance, even for very small clusters -->
<!-- # make assumptions of these methods explicit! -->
ORDER:

- summary
- congeniality, then in hierarchical models
- look whether we can fit cong. back in the main body
- alt. methods
- conclusion: mice is really easy!

@@

There are different strategies that can be adopted in the imputation process that account for clustering: inclusion of cluster indicator variable, performing a separate imputation process for each cluster, or performing a simultaneous imputation process by using an imputation method that accounts for clustering.(Stata: https://www.stata.com/support/faqs/statistics/clustering-and-mi-impute/) TODO: replace ref.

@@

Under this hierarchical imputation model, observations within clusters are correlated and this correlation is modeled by a random effect so the hierarchical model can be estimated even when there are few observations per cluster. However, this strategy is best suited for balanced data (Grund, 2017) and when random effects model is appropriated, i.e. the number of clusters is adequate. (Austin,2018).
